Guide to repository of supplementary resources

### 2022-11-25 index.Rmd
update index
Update Index

[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)

[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)

>>>>

[The repository on github, revision1 branch.](https://github.com/UZH-PEG/diversity_envresp1/tree/main)

[The respository on Zenodo with DOI 10.5281/zenodo.7360272](https://doi.org/10.5281/zenodo.7360272)
